\section{Conclusion \& Future Work}

We have conducted a multi-signal forensic audit of authorial identity decay under iterative LLM paraphrasing, addressing all three research questions:

\begin{enumerate}
    \item \textbf{RQ1: Layered erosion.} Different feature types erode at different rates. Lexical surface (BLEU) collapses at $T_1$; named entities (NER Recall) decay 5.8$\times$ faster than grammatical structure (POS cosine) as paraphrasing intensity increases. The ordering BERTScore $>$ POS cosine $>$ NER Recall $>$ ROUGE-L $>$ BLEU holds consistently across all tiers and paraphrasers.
    \item \textbf{RQ2: The point of no return.} Binary authorship attribution (Human vs.\ LLM) drops below random baseline (F1 $<$ 0.5) at $T_1$ for aggressive paraphrasers like Dipper (High). Conservative paraphrasers (Pegasus Slight) retain some signal through $T_3$. The point of no return depends on both the paraphraser's aggressiveness and the classifier's capacity.
    \item \textbf{RQ3: Forensic fingerprints.} A 6-class SVM achieves 75.5\% macro F1 in identifying which paraphraser was used, from delta features alone. Each paraphraser occupies a distinct position in the multi-dimensional feature space, with NER metrics and text compression being the most discriminative signals.
\end{enumerate}

Returning to the Ship of Theseus: after a single paraphrase iteration, the lexical planks are replaced, the entity cargo is partially jettisoned, but the grammatical hull and semantic meaning remain largely intact. A forensic examiner armed with POS distributions, NER metrics, and text statistics can both detect \emph{that} paraphrasing occurred and identify \emph{which} paraphraser was used---at least until the most aggressive settings erase all signal.

\textbf{Future work.} We plan to (1) compute SBERT embeddings for deeper semantic trajectory analysis; (2) extend attribution models to multi-tier evaluation with cross-paraphraser generalization; (3) investigate defense mechanisms that could make authorial identity more resistant to iterative paraphrasing; and (4) explore multilingual transfer of the erosion patterns observed in English.
