\section{Related Work}

\subsection{Authorship Attribution}

\citet{stamatatos2009survey} provides a comprehensive survey of modern stylometric approaches that use lexical, syntactic, and structural features to identify text authorship. The survey examines both traditional statistical methods and machine learning approaches for capturing distinctive writing patterns. Although these methods achieve strong performance on controlled datasets, the robustness of stylometric features under systematic text transformations remains an open question.

\citet{koppel2011authorship} investigate authorship attribution in real-world scenarios where authors may deliberately obfuscate their writing style. They demonstrate that text transformations such as paraphrasing, translation round-trips, and stylistic rewriting significantly degrade the performance of standard authorship attribution systems. While their work establishes that obfuscation is possible, it does not systematically quantify the rate of stylometric decay across iterative transformations---the central gap our work addresses.

More recent neural approaches use deep learning for authorship verification. Transformer-based models fine-tuned on author-specific corpora achieve strong closed-set attribution performance, and contrastive learning has been applied to learn author embeddings robust to topic variation. However, these methods have not been evaluated under iterative adversarial paraphrasing---a critical gap given that the features they learn (contextual representations of writing style) may degrade differently than hand-crafted stylometric features like POS distributions and punctuation patterns.

\subsection{AI-Generated Text Detection}

The rise of LLM-generated text has spurred work on automated detection. \citet{mitchell2023detectgpt} introduce DetectGPT, a zero-shot detection method based on probability curvature that distinguishes machine-generated from human-written text without requiring a trained classifier. \citet{kirchenbauer2023watermark} propose embedding statistical watermarks into LLM outputs during generation, enabling post-hoc detection via hypothesis testing. However, both approaches focus on identifying whether text was machine-generated, not on how iterative paraphrasing \emph{erodes} specific linguistic features at different rates. Plagiarism detection systems such as Turnitin and Copyleaks face a related but distinct challenge: they detect textual overlap rather than authorial signal, making them vulnerable to paraphrasing that preserves meaning while replacing surface features. Our work complements both detection and plagiarism research by characterizing \emph{what happens} to text features across paraphrase generations, which informs what signals detectors can rely on at each iteration depth.

\subsection{Paraphrasing and Style Transfer}

\citet{wahle2023paraphrase} develop a taxonomy of paraphrase types (morphological, lexical, syntactic, semantic, discourse) and show that different paraphrasers produce different distributions of paraphrase types. This motivates our investigation of paraphraser fingerprints (RQ3). \citet{krishna2023dipper} introduce the Dipper paraphraser with controllable diversity settings and demonstrate that even moderate paraphrasing evades most AI text detectors, though retrieval-based defenses remain effective. Their work provides the controlled paraphrasing tool central to our intensity experiments but does not measure how individual linguistic features (POS distributions, named entities) respond to the diversity dial. Notably, most paraphraser evaluations use single-domain benchmarks, leaving open whether findings generalize across registers and genres---a gap our seven-dataset analysis addresses.

\subsection{Evaluation Metrics}

\citet{papineni2002bleu} introduce BLEU, a precision-based metric for evaluating machine translation via n-gram overlap. \citet{lin2004rouge} presents ROUGE, a recall-oriented complement measuring content coverage. Both are purely lexical metrics: they measure surface word overlap, not semantic equivalence. \citet{zhang2020bertscore} propose BERTScore, which compares texts in contextual embedding space using DeBERTa, capturing meaning preservation beyond surface words. Our work combines all three metric types---lexical (BLEU, ROUGE-L), semantic (BERTScore), and structural (POS cosine, NER set overlap)---to provide a multi-dimensional view of how paraphrasing transforms text. This combination reveals that lexical and structural metrics can diverge sharply: a text can have near-zero BLEU (all words replaced) while retaining 0.88 POS cosine (grammatical structure preserved). Reporting only a single metric therefore conceals the feature-specific decay curves that are central to answering RQ1 and RQ2.
